\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}
\usepackage{url}
\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Braden Lockwood}}\\
  \href{https://mrbraden56.github.io}{Portfolio: mrbraden56.github.io} & Email: \href{mailto:}{bradenlock83@gmail.com}\\
  \href{https://github.com/mrbraden56}{Github: ~~github.com/mrbraden56} & Mobile:~~~816-419-3363 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
\resumeSubheading
  {Software Engineer}{}
  {Kiewit}{October 2023 - Present}
  \resumeItemListStart
    \resumeItem{}{Developed a company-wide safety app using React and TypeScript, streamlining the management of construction job safety processes.}
    \resumeItem{}{Managed the data and API within the safety app utilizing Python and Django, employing its ORM and REST framework.}
    \resumeItem{}{Proficient in SQL, efficiently interacting with complex stored procedures for efficient data querying.}
   \resumeItem{}{Effectively managed CI/CD pipelines using Azure DevOps and demonstrated a solid foundation in Azure for robust software deployment.}
    \resumeItem{}{Initiated the adoption of E2E and Integration testing strategies, enhancing software reliability and testing efficiency in the department.}
    \resumeItem{}{Implemented effective branching strategies in Git to optimize team collaboration and workflow management.}
  \resumeItemListEnd


\vspace{2pt}

      \resumeSubheading
		{Machine Learning Engineer}{}
		{Kiewit}{January 2023 -  October 2023}
		\resumeItemListStart
		\resumeItem{}{Engineered a Numpyro Bayesian Regression model, predicting equipment costs with 75\% accuracy and providing uncertainty estimates, enhancing strategic bidding and contract wins across U.S. transportation departments.}
		\resumeItem{}{Trained a series of XGBoost models using hand-crafted features to boost performance and optimized hyperparameters for efficient training.}
		\resumeItem{}{Pioneered a department-wide initiative at Kiewit by executing an automated data scraping strategy, resulting in over 9,000 engineering contracts being collected and subsequently utilized for a pivotal transportation cost prediction model.}
		\resumeItemListEnd

\vspace{2pt}
		
\resumeSubheading
    {Software Engineer Intern}{}
    {Kiewit}{May 2022 -  August 2022}
    \resumeItemListStart
    \resumeItem{}{Improved project management at Kiewit by developing an Angular-based web application, simplifying real-time tracking and storage of project requirements.}
    \resumeItem{}{Developed secure C\# ASP.Net Core APIs facilitating the storage and retrieval of project-specific images and sensitive data, enhancing the efficiency and security of data management.}
    \resumeItem{}{Established SQL databases using Entity Framework Core and database migrations for process simplification.}
    \resumeItem{}{Collaborated in an Agile software development team to produce efficient code.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

\resumeSubheading
  {Stython}{}
  {A Compiler for Python}{}
  \resumeItemListStart
    \resumeItem{}{Implemented a Hand-Coded Scanner using C++}
    \resumeItem{}{Designed the language using a series of regular expressions.}
  \resumeItemListEnd
		
		 \vspace{2pt}
  
    \resumeSubheading
		{NanoGrad}{}
		{A Smaller Implementation of Pytorch}{}
		\resumeItemListStart
	         \resumeItem{}{Initiated and developed a custom machine learning framework to deepen understanding of PyTorch internals.}
           \resumeItem{}{Employed Python for user interaction with the framework, emulating PyTorch's easy-to-use interface.}
           \resumeItem{}{Utilized modern C++ for the backend, optimizing matrix multiplication operations and memory management with smart pointers.}
        \resumeItem{}{Bridged Python frontend with C++ backend using ctypes library, and managed compilation with CMake, ensuring smooth and efficient performance.}

		\resumeItemListEnd
		
		 \vspace{2pt}
		 
    \resumeSubheading
    {Drewgon}{}
		{A Compiler Implemented in C++}{}
		\resumeItemListStart
		\resumeItem{}
	{Implemented the Scanner and Parser by using Flex and Bison.}
	\resumeItem{}
          {Optimized the intermidiate representation using techniques such as dead code elimiation and constant propagation}
          \resumeItem{}
          {Generated Assembly code for the x64 ISA, optimizing for efficient code by utlizing the memory zones.}
		\resumeItemListEnd
   
		

\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Kansas}{\textit{August 2018 - December 2022}}
      {B.S. Computer Science}{}
    \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~TypeScript, Python, Go, SQL, C\#, C++}
	\resumeSubItem{Frameworks}{~~~~React, Tanstack Query, Django, Numpy}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Git, SQL Server, Linux, Azure DevOps, Azure Pipelines}

\resumeSubHeadingListEnd

%-----------SKILLS-----------------
%\vspace{-5pt}
%\section{Goals}
%I am passionate about what I do and, wherever I go, I want to be around others who are passionate as well. I want to be constantly learning my entire life, willing to accept knowledge from whoever may give it.

\end{document}